### 2015-06-05 README.Rmd
Fixed in press link

(White TE, Dalrymple RL, Noble DWA, O’Hanlon JC, Zurek DB, Umbers KDL (2015) Reproducible research in the study of biological colouration. Animal Behaviour, in press)[http://dx.doi.org/10.1016/j.anbehav.2015.05.007]

>>>>

[White TE, Dalrymple RL, Noble DWA, O’Hanlon JC, Zurek DB, Umbers KDL (2015) Reproducible research in the study of biological colouration. *Animal Behaviour*, in press](http://dx.doi.org/10.1016/j.anbehav.2015.05.007)
